---
title: "FML"
author: "Aman"
date: "2024-01-31"
output:
  html_document: default
  pdf_document: default
---
## Executive summary - This dataset is about Electronic cards transection details which consist of the time period and Data value.
#Loading the dataset by assigning the variable name as Electroniic_cards
```{r}
Electronic_cards <- read.csv("C:/Users/amanp/OneDrive/Desktop/electronic-card-transactions-december-2023-csv-tables.csv")
Electronic_cards

```

## Performing descriptive statistics of quantitative and categorical variables.
```{r}
summary(Electronic_cards)
```
#Performing Summary analysis for Quantative variable
```{r}
summary(Electronic_cards$Data_value)
```
#Performing Summary analysis for categorical variable
```{r}
summary(Electronic_cards$UNITS)
```

```{r}
head(Electronic_cards)
```

```{r}
dim(Electronic_cards)
```
```{r}
str(Electronic_cards)
```
```{r}
class(Electronic_cards)
```


## Transforming the data in logical format 
```{r}
as.logical(Electronic_cards$Data_value)
```

## Plotting scatter plot for Data value and Period
```{r}
plot(Electronic_cards$Data_value, Electronic_cards$Period)
```

```{r}
## Plotting Histogram for Period
hist(Electronic_cards$Period)
```

